Finite element analysis ofmulti-dimensional and simplifiedmodels for beams and plates

### 2023-11-19 files/Chapter3/femconvergence.tex
chapter 32

Consider the Galerkin approximation for \eqref{GEVP}:
\subsubsection*{Problem $E_h$}
Find $u^h \in S^h$ such that \[b(u^h, v) = \lambda^h(u^h,v) \textrm{ for all } v \in S^h.\]

@@

Fix $m \in \mathbb{N}$. \label{sym:natural} Let $\left\{ \phi_i \in V | i = 1,2,...,m \right\}$ be a set of linear independent admissible basis functions. Define $S^h := \text{span}\left\{\phi_i \in V | i = 1,2,...,m\right\}$.

Since $S^h$ is finite dimensional, the ordering of the eigenvalues remains valid. The eigenvalues in the space $S^h$ is denoted as $\lambda_i^h$ with corresponding normalized eigenfunction $u^h_i$ for $i = 1,2,...,m$.

The space $S^h$\label{sym:Sh1} is a finite dimensional subspace of $V$. Therefore any subspace of $S^h$ will also be a subspace of $V$. So the minmax principle applies and a lower bound for the eigenvalues can be found:
\begin{equation}
	\lambda_i \leq \lambda_i^h.
\end{equation}

>>>>

Consider the Galerkin approximation for \eqref{GEVP}:
\subsubsection*{Problem $E_h$}
Find $u^h \in S^h$ such that $u^h \neq 0$ and \[b(u^h, v) = \lambda^h(u^h,v) \textrm{ for all } v \in S^h.\]

@@

Fix $m \in \mathbb{N}$. Let $\left\{ \phi_i \in V | i = 1,2,...,m \right\}$ be a set of linear independent admissible basis functions. Define $S^h := \text{span}\left\{\phi_i \in V | i = 1,2,...,m\right\}$ so that $S^h$ is a finite dimensional subspace of V. \label{sym:natural} \label{sym:Sh1}

The ordering of the eigenvalues remains valid in a finite dimensional space. The eigenvalues in the space $S^h$ is denoted as $\lambda_i^h$ with corresponding normalized eigenfunction $u^h_i$ for $i = 1,2,...,m$.

Also any subspace of $S^h$ will also be a subspace of $V$. So the minmax principle applies and a lower bound for the eigenvalues can be found:
\begin{equation}
	\lambda_i \leq \lambda_i^h.
\end{equation}
